---
output:
  word_document: default
  html_document: default
---
Gavarkavich 

#Prepare R Studio
```{r,echo=FALSE}
rm(list=ls())
library(tidyverse)
library(forcats)
library(ModelMetrics)
library(modelr)
library(caret)
load("els_train.RData")
load("els_test.RData")
load("els.RData")
```

#Assignment 5
To make it easier on myself and not have to go back and forth, I copied the code from assignment 5 below. 
```{r}
mod5<-lm(bynels2r~byses1,data=els_train) 
summary(mod5)
confint(mod5)
rmse_5<-modelr::rmse(mod5,els_test);rmse_5
mod6<-lm(bynels2r~as.factor(bypared)+
           byses1,
          data=els_train)
summary(mod6) 
els_train<-els_train%>%add_predictions(mod6)%>%rename(pred2=pred)
rmse_6<-modelr::rmse(mod6,els_test); rmse_6
```

#Assignment 10
##Problem 1 
10-fold cross validation of linear model predicting reading scores as function of at least 2 covariates; summary table or graphic of RMSEs from cross validation
```{r}
##In assignment 5, I used SES and parent education. I am using els not els_test or els_train.First I need to define the model

mod1_formula<-formula(bynels2r~byses1+
                        bypared)
basic.mod<-lm(mod1_formula,
              data=els); summary(basic.mod)

#Then apply kfold
els_cf<-els%>%
  crossv_kfold(10)
els_cf

rmse_mod1<-els_cf %>% 
  mutate(train = map(train, as_tibble)) %>% ## Convert to tibbles
  mutate(model = map(train, ~ lm(mod1_formula,
                                 data = .))) %>%
  mutate(rmse = map2_dbl(model, test, rmse)) %>% ## apply model, get rmse
  select(.id, rmse) ## pull just id and rmse 

summary(rmse_mod1$rmse)

gg<-ggplot(rmse_mod1,aes(rmse))
gg<-gg+geom_density()
gg
```


##Problem 2
Using random partition, create 100 separate cross validations 
```{r}
els_cv<-els%>%
  crossv_mc(n=100,test=.2)
els_cv

mod1_rmse_cv<-els_cv %>% 
  mutate(train = map(train, as_tibble)) %>% 
  mutate(model = map(train, ~ lm(mod1_formula, data = .)))%>%
  mutate(rmse = map2_dbl(model, test, rmse))%>% 
  select(.id, rmse)  

mod1_rmse_cv

summary(mod1_rmse_cv$rmse)

gg<-ggplot(mod1_rmse_cv,aes(rmse))
gg<-gg+geom_density(bins=50,fill="blue",alpha=.2)
gg

```

